Reanalysis Step 2: Multiple Imputation

### 2025-08-26 reanalysis-1-data_preparation.qmd
bugfix

@@

# Verify the temporal recoding worked correctly
verification_results <- data.frame(
  Check = c("Excluded cohort with outcome VA (should be 0)",
            "Submitted cohort with intermediate VA (should be 0)"),
  Count = c(
    sum(df_analysis$cohort_id == "excluded" & !is.na(df_analysis$outcome_VA_logMAR)),
    sum(df_analysis$cohort_id == "submitted" & !is.na(df_analysis$intermediate_VA_logMAR))
  ),
  Status = c(
    ifelse(sum(df_analysis$cohort_id == "excluded" & !is.na(df_analysis$outcome_VA_logMAR)) == 0, "✓ Pass", "✗ Fail"),
    ifelse(sum(df_analysis$cohort_id == "submitted" & !is.na(df_analysis$intermediate_VA_logMAR)) == 0, "✓ Pass", "✗ Fail")
  )
)

>>>>

    # For "submitted" cohort with observed outcome, use outcome as intermediate
    # If we have 2-year outcome, patient must have had intermediate value
    intermediate_VA_logMAR = if_else(
      cohort_id == "submitted" & !is.na(outcome_VA_logMAR),
      outcome_VA_logMAR,
      intermediate_VA_logMAR
    ),

@@

# Verify the temporal recoding worked correctly
n_submitted_with_outcome <- sum(df_analysis$cohort_id == "submitted" & !is.na(df_analysis$outcome_VA_logMAR))
n_submitted_with_intermediate <- sum(df_analysis$cohort_id == "submitted" & !is.na(df_analysis$intermediate_VA_logMAR))

verification_results <- data.frame(
  Check = c("Excluded cohort with outcome VA (should be 0)",
            "Submitted cohort: intermediate matches outcome count"),
  Count = c(
    sum(df_analysis$cohort_id == "excluded" & !is.na(df_analysis$outcome_VA_logMAR)),
    paste(n_submitted_with_intermediate, "vs", n_submitted_with_outcome)
  ),
  Status = c(
    ifelse(sum(df_analysis$cohort_id == "excluded" & !is.na(df_analysis$outcome_VA_logMAR)) == 0, "✓ Pass", "✗ Fail"),
    ifelse(n_submitted_with_intermediate == n_submitted_with_outcome, "✓ Pass", "✗ Fail")
  )
)

### 2025-08-26 reanalysis-2-multiple_imputation.qmd
bugfix

- **Baseline VA:** Starting point for temporal chain
- **Intermediate VA:** Bridge between baseline and 2-year outcome
- **Outcome VA:** Final 2-year outcome (missing for 'excluded' cohort)
- **Temporal order enforced:** baseline → intermediate → outcome
- **No reverse-time prediction allowed**

>>>>

- **Baseline VA:** Starting point for temporal chain
- **Intermediate VA:** Bridge between baseline and 2-year outcome
  - For "submitted" cohort with observed outcome: set to outcome value
  - For "excluded" cohort: contains observed intermediate follow-up values
  - Reduces missing data substantially compared to leaving as NA
- **Outcome VA:** Final 2-year outcome (missing for 'excluded' cohort)
- **Temporal order enforced:** baseline → intermediate → outcome
- **No reverse-time prediction allowed**
